\begin{thebibliography}{99}

\bibitem{kaplan1958}
Kaplan E L, Meier P. Nonparametric estimation from incomplete observations[J]. \emph{Journal of the American Statistical Association}, 1958, 53(282): 457--481.

\bibitem{cox1972}
Cox D R. Regression models and life-tables[J]. \emph{Journal of the Royal Statistical Society: Series B (Methodological)}, 1972, 34(2): 187--202.

\bibitem{kleinbaum2012}
Kleinbaum D G, Klein M. \emph{Survival Analysis: A Self-Learning Text}[M]. 3rd ed. New York: Springer, 2012: 1--700.

\bibitem{chen2016}
Chen T, Guestrin C. XGBoost: A scalable tree boosting system[C]. \emph{Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, San Francisco, 2016: 785--794.

\bibitem{lundberg2017}
Lundberg S M, Lee S I. A unified approach to interpreting model predictions[C]. \emph{Advances in Neural Information Processing Systems (NeurIPS)}, Long Beach, 2017: 4765--4774.

\bibitem{belotti2015twopm}
Belotti F, Deb P, Manning W G, et al. twopm: Two-part models[J]. \emph{The Stata Journal}, 2015, 15(1): 3--20.

\bibitem{macqueen1967}
MacQueen J. Some methods for classification and analysis of multivariate observations[C]. \emph{Proceedings of the 5th Berkeley Symposium on Mathematical Statistics and Probability}, Berkeley, 1967, 1(14): 281--297.

\bibitem{hammersley1964}
Hammersley J M, Handscomb D C. \emph{Monte Carlo Methods}[M]. London: Methuen, 1964: 1--178.

\bibitem{ascarza2025}
Ascarza E, Netzer O, Runge J. Personalized game design for improved user retention and monetization in freemium mobile games[J]. \emph{International Journal of Research in Marketing}, 2025, 42(4): 975--995.

\bibitem{wei2024}
Wei Z, Liu Y, Zhang H, et al. Multi-treatment multi-task uplift modeling for enhancing user growth[J/OL]. \emph{arXiv preprint arXiv:2408.12803}, 2024. \url{https://arxiv.org/abs/2408.12803}. 访问时间: 2026年5月24日.

\bibitem{pape2024}
Pape P, Hekimo\v{g}lu M, Wierenga B. Personalized content, engagement, and monetization in a mobile puzzle game[J]. \emph{International Journal of Research in Marketing}, 2024, 41(3): 528--546.

\end{thebibliography}
